---
title: "Simulation Distribution"
output: html_notebook
---

Generate realistic sample set for the equation to test distribution of +/- values and see if it makes sense 

Equation: y = (theta1 * x1) + (theta2 * x2) + ... + (theta7 * x7)

- x being the form inputs (-1, 0 , 1)
- theta being weights we decided
- x is what we want to simulate 

Install tidyverse from CRAN

```{r}
install.packages("tidyverse")
```

Load packages. modelr package wraps around base R’s modelling functions to make them work naturally in a pipe

```{r}
library(tidyverse)

library(modelr)
options(na.action = na.warn)
```

Assumptions:

- An answer is equally likely it will be -1, 0, or 1, because we don’t know the probability for a user to choose one answer over another for a given question
- Each question is independent of each other. Meaning, the answer to one question has no effect on another


```{r}
# Setup and initializations
theta <- c(
  15.861187, # Emotional/Mental (yes)
  8.362460625, # Physical Health (yes)
  -6.45491, # Allergies (yes)
  25.568928, # Age (old)
  4.3575, # Age (child)
  29.339743, # House (yes)
  3.778483333, # Family (alone)
  3.33245, # Family (not alone)
  2.0, # Prior Ownership (yes)
  -44.7118 # Can't afford Avg $ Cost of dog (yes)
)
df <- data.frame(
  mental=integer(), # Emotional/Mental (0 = no, 1 = yes)
  physical=integer(), # Physical Health (0 = no, 1 = yes)
  allergies=integer(), # Allergies (0 = no, 1 = yes)
  age=integer(), # Age (child, adult, elderly, very elderly)
  house=integer(), # House (0 = no, 1 = yes)
  family=integer(), # Family (alone, not alone)
  owner=integer(), # Prior Ownership (0 = no, 1 = yes)
  financial=integer(), # Can't Afford (0 = no, 1 = yes)
  y=double()) # score (outcome)
header <- c("mental", "physical", "allergies", "age", "house", "family", "owner", "financial", "score")
N <- 100 # sample size (num of rows)

for (i in 1:N) {
  # Generate random user inputs
  mental <- sample(0:1, 1) * theta[1]
  physical <- sample(0:1, 1) * theta[2]
  allergies <- sample(0:1, 1) * theta[3]
  age <- sample(1:4, 1)
  if (age == 1) {
    age <- theta[4]
  } else if (age == 2) {
    age <- theta[5]
  } else {
    age <- 0
  }
  house <- sample(0:1, 1) * theta[6]
  family <- sample(0:1, 1)
  if (family == 0) {
    family <- theta[7]
  } else {
    family <- theta[8]
  }
  owner <- sample(0:1, 1) * theta[9]
  financial <- sample(0:1, 1) * theta[10]

  # Combine into equation
  x <- matrix(c(mental, physical, allergies, age, house, family, owner, financial), nrow = 1)
  y <- sum(x)
  
  # Add row to dataframe
  df.new = data.frame(x, y)
  df <- rbind(df, df.new)
}

# Update header
colnames(df) <- header

# Add numeric user id, as each row represents one user
df$id <- seq.int(nrow(df))

# Calculate average score
avg.score <- sum(df$score)/N
avg.score

# Graph distribution of users and their outcomes
ggplot(df, aes(id, score)) + 
  xlab("User") +
  ylab("Score") +
  geom_point() +
  geom_hline(yintercept = avg.score, colour = 4) +
  geom_hline(yintercept = 0, colour = 2)

```











