---
title: "Dog name analysis"
output: html_notebook
---


This code groups dog name data by breed name and sorts by the breed name alphabetically and count of the animal name descending
```{r}
library(dplyr)
dogdata = read.csv("dogNamesCleaned.csv")

breedData <- group_by(dogdata, BreedName, AnimalName) %>% tally(sort = T) %>% ungroup() %>% group_by(BreedName) %>% arrange(desc(n)) %>% arrange(BreedName)

```

This code calculates the average length of dog name overall, which is 4 characters 
```{r}
x <- c(dogdata$AnimalName)
dogdata$length = nchar(x)
dogdata <- dogdata %>% filter(!is.na(AnimalName))
meanNameLength <- mean(dogdata$length)
```

This code sorts by most popular dog names overall
```{r}
popularData <- group_by(dogdata, AnimalName) %>% tally(sort = T) %>% ungroup() %>% group_by(AnimalName) %>% arrange(desc(n))
  
```

This code sorts by most popular girl dog names
```{r}
popularGirlData <- group_by(dogdata, AnimalGender, AnimalName) %>% filter(AnimalGender == 'F') %>% tally(sort = T) %>% ungroup() %>% group_by(AnimalGender) %>% arrange(desc(n))
```

This code sorts by most popular boy dog names
```{r}
popularBoyData <- group_by(dogdata, AnimalGender, AnimalName) %>% filter(AnimalGender == 'M') %>% tally(sort = T) %>% ungroup() %>% group_by(AnimalGender) %>% arrange(desc(n))
```

This code calculates the most popular dog names per borough

```{r}
boroughData <- group_by(dogdata, Borough, AnimalName) %>% tally(sort = T) %>% ungroup() %>% group_by(Borough) %>% arrange(desc(n)) %>% arrange(Borough)
```

